### 2017-01-03 paper/evaluation.tex
Added research question
Fixed RQs ordering

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
regression test suites in open-source projects?}
\newcommand{\RQB}{How often are parallelization features in
build files?}
\newcommand{\RQC}{What is the impact of parallalelization?}

\newcommand{\RQD}{What factors contribute to improve performance
through parallelization?\Jbc{Previously as "When does parallelization
works and when it does not so great?"}}

\newcommand{\RQE}{What are the limitations of parallelization?}

\newcommand{\rqOne}{\textbf{RQ1.} \RQA}
\newcommand{\rqTwo}{\textbf{RQ2.} \RQB}
\newcommand{\rqThree}{\textbf{RQ3.} \RQC}
\newcommand{\rqFour}{\textbf{RQ4.} \RQD}
\newcommand{\rqFive}{\textbf{RQ5.} \RQE}

\begin{itemize}
    \item \rqOne
    \item \rqTwo
    \item \rqThree
    \item \rqFour
    \item \rqFive
\end{itemize}

@@

The first research question addresses the prevalence of long-running
test suites. We are interested to know if costly test suites are
common in open-source projects.  The second research question
addresses our interest in understanding if developers are aware of
parallelization features from testing frameworks available
out-of-the-box through build systems (\eg, run JUnit test cases in
parallel using Maven Surefire) and what setting are more often used.
The third research question addresses the impact of parallelism on the
regression tests from our sample set. For subjects that use
parallelization settings, we are interested in compare the execution
performance when these settings are activated and deactivated (\ie,
sequential execution). The fourth research question addresses the
characteristics of regression tests from the previous experiment.
More specifically, we want to investigate if there is a relation
between the balance of test execution (\ie, how uniformly distributed
is the execution time across tests cases) and the usage of
computational resources (\ie, if tests are mostly CPU or IO intense)
that impacts the effectiveness of parallelization. Finally, the fifth
research question discusses the limitations and insights to overcome
the pitfalls of parallelization.

@@

\subsection{Answering research question RQ2}
\label{sec:rqTwo}

@@

To evaluate the presence of parallelization settings, we considered
the \numSubjsRqTwo{} subjects from the groups \emph{long} and
\emph{medium} identified in Section~\ref{sec:rqone}. We focused on
these two groups because given that costly test suites exist, we
wanted to analyze if their maintainers are aware of parallelization
settings and how they use these settings.  We computed the
frequency of the parallelism modes (see Section \ref{sec:modes}) using
a semi-automatic approach: we first discover automatically the
relevant build files (\ie, \emph{pom.xml} files) and then we manually
inspect them to eliminate false-positves (\eg, commented
configuration).  Figure~\ref{fig:discovery-step} describes the
discovery step: first, we list the paths of all build file and then we
filter only the build files that contain any of the keywords,
\CodeIn{forkMode}, \CodeIn{forkCount}, or \CodeIn{parallel}. Notice
that, for Maven projects, any of these keywords exist in any possible
parallelism configuration \Fix{cite surefire doc}.

@@

\subsection{Answering research question RQ3}
\label{sec:rqThree}

>>>>

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
regression test suites in open-source projects?}
\newcommand{\RQB}{How the time cost from a test suite is distributed
among the test cases?}
\newcommand{\RQC}{How often are parallelization features in
build files?}
\newcommand{\RQD}{What is the impact of parallalelization?}
\newcommand{\RQE}{What factors contribute to improve performance
through parallelization?\Jbc{Previously as "When does parallelization
works and when it does not so great?"}}
\newcommand{\RQF}{What are the limitations of parallelization?}

\newcommand{\rqA}{\textbf{RQ1.} \RQA}
\newcommand{\rqB}{\textbf{RQ2.} \RQB}
\newcommand{\rqC}{\textbf{RQ3.} \RQC}
\newcommand{\rqD}{\textbf{RQ4.} \RQD}
\newcommand{\rqE}{\textbf{RQ5.} \RQE}
\newcommand{\rqF}{\textbf{RQ6.} \RQF}

\begin{itemize}
    \item \rqA
    \item \rqB
    \item \rqC
    \item \rqD
    \item \rqE
    \item \rqF
\end{itemize}

@@

The first research question addresses the prevalence of long-running
test suites. We are interested to know if costly test suites are
common in open-source projects. The second research question addresses
the balance of regression tests. We want to investigate how the time
cost of a test suite is distributed among test cases. The third
research question addresses our interest in understanding if
developers are aware of parallelization features from testing
frameworks available out-of-the-box through build systems (\eg, run
JUnit test cases in parallel using Maven Surefire) and what setting
are more often used.  The fourth research question addresses the
impact of parallelism on the regression tests from our sample set. For
subjects that use parallelization settings, we are interested in
compare the execution performance when these settings are activated
and deactivated (\ie, sequential execution). The fifth research
question addresses the characteristics of regression tests from the
previous experiment.  More specifically, we want to investigate if
there is a relation between the balance of test execution (\ie, how
uniformly distributed is the execution time across tests cases) and
the usage of computational resources (\ie, if tests are mostly CPU or
IO intense) that impacts the effectiveness of parallelization.
Finally, the sixth research question discusses the limitations and
insights to overcome the pitfalls of parallelization.

@@

\subsection{Answering research question RQ2}
\label{sec:rqB}

@@

\Fix{to appear}

\subsection{Answering research question RQ3}
\label{sec:rqC}

To evaluate the presence of parallelization settings, we considered
the \numSubjsRqTwo{} subjects from the groups \emph{long} and
\emph{medium} identified in Section~\ref{sec:rqA}. We focused on
these two groups because given that costly test suites exist, we
wanted to analyze if their maintainers are aware of parallelization
settings and how they use these settings.  We computed the
frequency of the parallelism modes (see Section \ref{sec:modes}) using
a semi-automatic approach: we first discover automatically the
relevant build files (\ie, \emph{pom.xml} files) and then we manually
inspect them to eliminate false-positves (\eg, commented
configuration).  Figure~\ref{fig:discovery-step} describes the
discovery step: first, we list the paths of all build file and then we
filter only the build files that contain any of the keywords,
\CodeIn{forkMode}, \CodeIn{forkCount}, or \CodeIn{parallel}. Notice
that, for Maven projects, any of these keywords exist in any possible
parallelism configuration \Fix{cite surefire doc}.

@@

\subsection{Answering research question RQ4}
\label{sec:rqD}

\begin{itemize}
    \item \emph{\RQD}
\end{itemize}
